\documentclass[a4paper,12pt]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{pdfpages}

% one-and-a-half line spacing as specified in the assessment description
\usepackage{setspace}
\onehalfspacing

% The package to configure the enumerate environment
\usepackage{enumitem}

\usepackage{url}

\usepackage[left=2cm,right=2cm,top=2cm,bottom=3cm]{geometry}


\begin{document}

\title{Evaluation Expert 3}
\date{March 27, 2011}
\author{Irem Tanriseven}
\maketitle

\section{Key-Level Model (KLM) Analysis}
According to the following scenario, there are time measurements for all operators so as to measure the efficiency of our webshops design.

\subsection{Scenario}
Susan, 82 years old, would like to buy trousers online. Her niece Pam gave birth to an adorable girl just three months ago. Since Susan is invited to go over to Pam's place for dinner, she would like to bring along a present for her. Pam's mentioned that her girl just grew out of another pair of trousers, so Susan would like to get her a new one. She would like to order a nice one, but it should't be too pricey. Susan knows that Pam likes yellow, which is why the trousers should be yellow if possible.

\subsection{Assumptions}
Susan got her first computer two years ago, but she doesn't use it very often. She's ordered groceries online before, but she's never ordered anything from our shop. She doesn't like to create accounts and always pays with credit card, where possible.

\subsection{Actions to buy trousers for a girl}

\begin{enumerate}
  \item Move hand to mouse (H) 0.4 sec
  \item Mentally prepare to search for girl trousers (M) 9 sec
  \item Point to girls label then bottom label and trousers label (P) 1.1 sec
  \item Mentally prepare to select a girl trouser among the trouser pictures (M) 9 sec
  \item Points to one of the trousers  for looking the details of it (P) 0.2 sec
  \item Look through the details of the item (M) 9 sec
  \item Choose the color and size of the item (M) 9 sec
  \item Point to Add Cart button (P) 0.2 sec
  \item Look through the details of the Your Cart (M) 9 sec
  \item Mentally decide either continue shopping or checkout (M) 9 sec
  \item Point to Checkout button (P) 0.2 sec
  \item Mentally prepare to select one of the options (Sign In, Create new account, Guest Checkout) (M) 9 sec
  \item Point Guest Checkout label (P) 0.2 sec
  \item Choose the preferred payment option (M) 9 sec
  \item Fill in credit card details (F) 15 sec
  \item Review and place order (M) 9 sec
  \item Look through Confirmation screen (M) 9 sec
\end{enumerate}


$Time=H+10M+5P+F=.4+10*9+(5*0.2)+15 = 106.4 sec$

\end{document}