\section{Task analysis and scenarios}

\subsection{Hierarchical tasks model}

To create our task model, we have analyzed different websites for baby clothes, like \textit{oshkoshbgosh.com} or \textit{mybabyclothesboutique.com}, as well as websites for adult clothes (\textit{fashion.warehouse.co.uk}, etc).

\subsubsection{Buy baby clothes}
\begin{enumerate}[label*=\arabic*.,start=0,itemsep=-4pt]
  \item In order to buy baby clothes in the Web shop :
  \item Find an item 
    \begin{enumerate}[label*=\arabic*.,itemsep=-4pt]
      \item Search for a specific item (by name or reference)
      \item Browse through all items
				\begin{enumerate}[label*=\arabic*.,itemsep=-4pt]
				  \item Sort by category, price, name, size or availability
        \end{enumerate}
    \end{enumerate}
  \item Select an item and get more details for it
  \item Add item to the shopping cart
    \begin{enumerate}[label*=\arabic*.,itemsep=-4pt]
      \item Select size, color and quantity
    \end{enumerate}
  \item See items in shopping cart
    \begin{enumerate}[label*=\arabic*.,itemsep=-4pt]
      \item Delete items
      \item Change quantity, size or color for all items
    \end{enumerate}
  \item Go to check out
    \begin{enumerate}[label*=\arabic*.,itemsep=-4pt]
      \item Confirm shopping items or delete items
      \item Log in with user name and password, or create a new account, or continue without account
      \item Select address and name
	\begin{enumerate}[label*=\arabic*.,itemsep=-4pt]
	  \item Choose a personal data set among all personal data 
	  \item Provide personal data (name, street, city, country, phone number, email address)
        \end{enumerate}
      \item Select payment method
      \item Confirm order      
    \end{enumerate}
  \item Log out
\end{enumerate}
Plan 1: repeat 1-2-3-4-5 in this order for all different purchases you wish to make\\
Plan 1.1: do (1.1) or (1.2); (1.2.1) is not mandatory\\
Plan 5: do (5.2) if not already logged in; do (5.2), (5.3.1) and (6) only if user account exists\\
Plan 5.2: three possibilities: log in, create a new account (go to "create a customer account" task) or continue without an account; do (5.3.2) only for a new account, or if checking out without account

\subsubsection{Create a customer account}
\begin{enumerate}[label*=\arabic*.,start=0,itemsep=-4pt]
  \item In order to create a customer account:
  \item Enter login information
  \begin{enumerate}[label*=\arabic*.,itemsep=-4pt]
		\item Provide a user name
		\item Provide a password
	\end{enumerate}
  \item Provide personal data (name, street, city, country, phone number, email address)
  \item Save account
\end{enumerate}
Plan 1: do 1-2-3 in this order\\
Plan 1.1: repeat 1.1 and 1.2 until user name and password are accepted

\subsubsection{Manage an account}
\begin{enumerate}[label*=\arabic*.,start=0,itemsep=-4pt]
  \item In order to manage a customer account:
  \item Log in with user name and password
  \item Look at history of orders
  \item Change personal data
    \begin{enumerate}[label*=\arabic*.,itemsep=-4pt]
      \item Edit data
      \item Save data
    \end{enumerate}
%  \item Go to special offers page
\end{enumerate}
Plan 1: do 1 and then 2 and 3 independently
%Plan 5: go to "buy baby clothes" task (2.b) but with special offers

\subsection{Scenarios}
\textbf{Jeff and Judy Seavers} would like to surprise their daughter with a complete set of baby clothes.
Because Julie just had a girl, they would like to buy primarily pink or red clothes. Cost isn't that important, since the clothes will be a present for their daughter.
They would like to get the ordered clothes before their daughter leaves the hospital in about four days, so they need to be able to learn how to navigate through the online shop as quickly as possible and sort the products by availability.

\textbf{Sarah Gordon} still has most of the baby clothes from her first child. She only needs a new romper suit.
Due to the fact that she does not have much money, the romper suit should be as cheap as possible.
However, she wants her child to look cute, so she would like to find a suit with a hood and attached ears.

\textbf{Bruce Walker} is on the lookout for some nice baby clothes to give to his niece for her third birthday.
He doesn't really know what he wants but he always thinks that babies in yellow clothes look particularly cute, so he would like to buy yellow clothes.
Because his sister's baby will have her first birthday in about 2 weeks, he needs to have the clothes until then.

%\textbf{Greg Campbell} would really like to buy a suit for Lisa's son. But after a couple of talks with Lisa, he realised that a shirt and some pants would be better suited.
%He likes prints on his shirts, so he would like to find a shirt with the words "Rock Star" printed on it.
%Finding a nice shirt is more important to him than the price, but he wishes not to spend more than \pounds20 at the moment, including delivery.