\section{Prototype}

For represented our prototype, we have designed a series of screen sketches, build with Microsoft PowerPoint. Because we would like our prototype to be easy to change (by designers or by users),
% rephrase if still needed -> 
%to create and to simulate the prototype 
we have decided to implement it in a low fidelity. The Powerpoint slides are in the appendix (slide 1 to 15).

\subsection{Find and select an item}
The first slide shows the home page of our website. By clicking on one of the buttons of the global systems menus, the user can access to the corresponding local systems menus (as defined in~\ref{sec:local_systems}) and thus obtain the corresponding list of items (for example: click on ``Boy'', then on ``Trousers'' and obtain the list of boy trousers). Here, the user has the possibility to sort the items using the "Order by" lists, and clicking and the "Go" button. On top of the filters found in the questionnaires, we also provide ``Availability'' for people who're only interested in products that can be delivered in a certain time range. If there are many pages containing items, the user can browse each of them thanks to the "Previous" and "Next" buttons (on the bottom). Use the "Search bar", and click on "Find", is another way for finding a specific item.

When the user selects an item, a new page appears with its description (price, picture, size, etc). 
The ``Add to cart'' button adds the item to the user's shopping cart.

\subsection{Buy an item}
When the user wants to buy the items he put into his cart, the user has to select the "Cart" button (as defined previously, to be logged is not mandatory). In the cart view, the user has an overview of each item and can change the previously selected quantity, colour and size. He can then continue his shopping, "Continue shopping" button, or proceed to payment, with the "Checkout" button.

From now, we suppose that the customer doesn't want to be register and has selected "Checkout". The Checkout page is then shown (slide 10) and the user has to select "Guest Checkout". From the step 1 to 3 of his Checkout, the user must to fill his shipping and payment informations. The final step is to review and place his order. If everything is correct, the confirmation page is shown (slide 15).
